\thispagestyle{empty}
\pdfbookmark{Acknowledgments}{Acknowledgments}

\begin{acknowledgments} 

First would like to thank IST for being my home and teaching me everything I needed to get this far. It has been truly amazing studying here and knowing so many inspiring teachers and so many brilliant colleagues.\\
\par A huge thank you goes to my supervisor and teacher Doctor Ana Moita, for introducing me to the experimental world as well as all the patience, support and time that she put into my work. I'd also like to thank Emanuele Teodori for answering to all my questions and guiding me through every decision, even when far away. I'd also like to thank my professor and co-supervisor Doctor António Moreira for having me in his laboratory team.\\
\par A big acknowledgment goes also to my laboratory mates who helped me in countless occasions and kept me motivated. I'd like to give a special thank you to all the boiling team that gave great input into my work.\\
\par I'd like to give a special thank you to Henrique Carvalho, for being my electronics consultant and Vasco Rodrigues for the mechanical piece he made for me. Without them this thesis would be a lot harder. To all my other friends that helped me and motivated me I'd also like to say thank you.\\
\par This work couldn't also be done without workshop professor Manuel Venes and his colleague welding professor, for helping me welding the blackbody. For the device's box I need to thank my good friend Paulo Belga. Also, for all the support and help, I need to thank João and Pedro from LTO.\\
\par Finally for the constant patience and support, I'd like to thank my family. And last but not least I'd like to thank my girlfriend, Tânia for keeping me company during my writing sessions but mostly for all the love and support.

% Agradece tb por cortesia ao Prof Moreira, por te ter recebido na equipa do laboratório e na qualidade de teu co-orientador (por questões burocraticas)%
\end{acknowledgments}

% \hbox{} \vfill
% \begin{flushright}
% \small \textit{\textbf{"Try not to become a person of success, but rather try to become a person of value."}} %%% MUDAR %%%
% \\ \vspace{2mm}  
% \scriptsize Albert Einstein
% \end{flushright}

\clearpage
\thispagestyle{empty}
\cleardoublepage